Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2015-12-04 jss/article.tex
[skip ci] jss update
Added enrichment default values

>>>>

[explain default values]\\
The \code{maps} argument can either be a dataframe imported from a gmt file with the \code{format_from_gmt} function or a list of dataframes generated by the same procedure. By default, the function uses the ACSN maps previously described.

The correction for multiple testing by default is set to false discovery rate (fdr), which is equivalent to Benjamini \& Hochberg correction, but can be changed to any of the usual corrections such as Bonferroni, Holm, Hochberg, Holm, or Benjamini \& Yekutieli \cite{Benjamini2003FDR}, or even disabled .

The minimal module size represents the smallest size value of a module that will be used to compute enrichment or depletion. This is meant to remove results of low significance for module of small size.

The universe in which the computation is made by default is defined by the maps. Which means that all genes that were given as input and that are not present on the maps will be discarded. To keep all genes, the user can set the universe to \code{HUGO},referring to the database.

The threshold is the maximal value of the corrected p-value (unless user chose not to correct for multiple testing) that will be displayed in the result table.

[give examples with maps, universe, correction multtest]

[explain multiple samples]

[explain graphs generation]
